Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-19 paper/ms.tex
add image processing figure

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.3\textwidth]{pipelineoverview.pdf}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    Conceptual overview of photometric reduction pipeline.
    Details are given in \S~\ref{sec:method}.
    %TODO: add latex section numbers!
    %TODO: do FORCED aperture photomery on differenced images
    %TODO: improve text generally
	\label{fig:pipeline}
	}
\end{figure}

@@

In order to pre-emptively address the background variations present in
some frames due to scattered light from the Earth and Moon
\citep[see][\S 7.3.1--7.3.4]{vanderspek_2018}, we then estimate and
subtract the large-scale background.  We do this by temporarily
masking out pixels more than $2\sigma$ from the image median, and then
pass a $48\times48$ median box filter over each pixel in the image,
with reflective boundary conditions.  The resulting background
estimate has low-amplitude structure over spatial scales of a few
pixels, so we then blur it with a gaussian kernel to produce a smooth
background estimate for each image.  These steps also remove a
low-level vignetting present in the corners of many images, which
remains even after flat-fielding \citep[see][\S
7.3.5]{vanderspek_2018}.  With the exception of scattered light
patches, which remain over small areas of less than 10\% of the
frames, our ad-hoc procedure seems to adequately remove large spatial
scale scattered light patches.

@@

The procedure described above was first proposed by \citet{Alard_Lupton_1998}.
It was reviewed and clarified by \citet{miller_optimal_2008}.
The choice of how to decompose the kernel was further explored by
\citet{bramich_new_2008}, who showed that using a linear combination
of delta functions had advantages compared to a basis of gaussians.
We perform the convolution using \texttt{ficonv}, and opt for the
implementation of Bramich's method (see \citealt{Pal_2009} \S~2.8).

\subsubsection{Astrometric registration}
We now describe a few implementation details we used to make the
above high-level picture work.
First, we needed to select two ``reference frames'' for image subtraction:
(1) the astrometric reference; and (2) the photometric reference.

@@

\acknowledgements
L.G.B.\ gladly acknowledges helpful discussions with
C Huang, M Soares-Furtado, ...
..., and is
grateful to the people who have turned TESS from an idea into reality.
%
J.N.W.\ thanks ...
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
This research has made use of the NASA Exoplanet Archive, which is
operated by the California Institute of Technology, under contract
with the National Aeronautics and Space Administration under the
Exoplanet Exploration Program.
%
This work made use of NASA's Astrophysics Data System Bibliographic
Services.
%
This research has made use of the VizieR catalogue access tool, CDS,
Strasbourg, France. The original description of the VizieR service was
published in A\&AS 143, 23.
%
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral
Agreement.
%
The Digitized Sky Surveys were produced at the Space Telescope Science Institute under U.S. Government grant NAG W-2166. The images of these surveys are based on photographic data obtained using the Oschin Schmidt Telescope on Palomar Mountain and the UK Schmidt Telescope. The plates were processed into the present compressed digital form with the permission of these institutions.
%
\newline
%
\facility{
	2MASS \citep{skrutskie_tmass_2006},
	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018},
	TESS \citep{ricker_transiting_2015},
	UCAC4 \citep{zacharias_fourth_2013}
    %DSS (CITE)    
}
%
\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  \texttt{astropy} \citep{the_astropy_collaboration_astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{astroquery.gaia} CITE,
  %\texttt{astroquery.simbad} CITE,
  %\texttt{astroquery.mast} CITE,
  %\texttt{astroquery.nasaexopanetarchive} CITE,
  \texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{corner} \citep{corner_2016},
  \texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{fitsh} \citep{Pal_2012},
  \texttt{IPython} \citep{perez_2007},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{serven_pygam_2018_1476122}
  \texttt{psycopg2} (\url{initd.org/psycopg})
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{TagSpaces} (\url{tagspaces.org}),
  \texttt{tesscut} \citep{brasseur_astrocut_2019},
  \texttt{VARTOOLS} \citep{Hartman_Bakos_2016}
  \texttt{wotan} \citep{hippke_wotan_2019},
}

>>>>

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.3\textwidth]{pipelineoverview.pdf}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    Conceptual overview of photometric reduction pipeline.
    Details are given in \S~\ref{sec:method}.
    %TODO: add latex section numbers!
    %TODO: do FORCED aperture photomery on differenced images
    %TODO: improve text generally
	\label{fig:pipeline}
	}
\end{figure}

\begin{figure*}[!t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.95\textwidth]{stages_of_image_processing_good.png}
    \end{center}
    \vspace{-0.6cm}
    \caption{
        Stages of image processing for an image taken during the middle
        of an orbit.
        {\it Top right}. Calibrated image.
        {\it Top left}. Smooth background estimate.
        {\it Middle right}. Calibrated image minus its median pixel value.
        {\it Middle left}. Calibrated image minus smooth background.
        {\it Bottom left}. Registered difference image.
        {\it Bottom right}. Zoom of difference image.
        Each image is $(2048\times2048)$ pixels, except for the bottom-right 
        image, which is $(500\times500)$.
        All images except the top-right have the same color map.
        The sector, camera, and CCD are (6, 1, 2).
        \label{fig:stages_good}
    }
\end{figure*}

\begin{figure*}[!t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.95\textwidth]{stages_of_image_processing_bad.png}
    \end{center}
    \vspace{-0.6cm}
    \caption{
        Same sector, camera and CCD as Figure~\ref{fig:stages_good}, but for an image taken during
        perigee passage, when scattered light from the Earth is
        prominent.
        A number of systematic artifacts are present,
        including vertical ``straps'' and small-scale structure in scattered light
        patches.
        The quality of astrometric registration in the difference image is also
        worse, leading to larger residuals in the lower-right panel.
        \label{fig:stages_bad}
    }
\end{figure*}

@@

In order to preemptively address the background variations present in
some frames due to scattered light from the Earth and Moon
\citep[see][\S 7.3.1--7.3.4]{vanderspek_2018}, we then estimate and
subtract the large-scale background.  We do this by temporarily
masking out pixels more than $2\sigma$ from the image median, and then
pass a $48\times48$ median box filter over each pixel in the image,
with reflective boundary conditions.  The resulting background
estimate has low-amplitude structure over spatial scales of a few
pixels, so we then blur it with a gaussian kernel to produce a smooth
background estimate for each image.  These steps also remove a
low-level vignetting present in the corners of many images, which
remains even after flat-fielding \citep[see][\S
7.3.5]{vanderspek_2018}.  
The results are shown in the upper four panels of Figures~\ref{fig:stages_good}
and~\ref{fig:stages_bad}.
Features with spatial scales smaller than $\approx$48 pixel remain, 
and large spatial scale scattered light patches are removed.

@@

The general procedure described above was first proposed by \citet{Alard_Lupton_1998}.
It was reviewed and clarified by \citet{miller_optimal_2008}.
The choice of how to decompose the kernel was further explored by
\citet{bramich_new_2008}, who showed that using a linear combination
of delta functions had advantages compared to a basis of gaussians.
We perform the convolution using \texttt{ficonv}, and opt for the
implementation of Bramich's method (see \citealt{Pal_2009} \S~2.8).
The lower panels of
Figure~\ref{fig:stages_good} show the procedure
working well, and producing a ``clean'' difference image.
Figure~\ref{fig:stages_bad} shows what happens for an
image taken when scattered light from the Earth causes the
model image $M_{xy}$ to be a poor fit to the target image $I_{xy}$, 
leading to a number of systematic artificats.

\subsubsection{Astrometric registration}
We now describe some implementation details we used to make the
above high-level picture work.
First, we needed to select two ``reference frames'' for image subtraction:
(1) the astrometric reference; and (2) the photometric reference.

@@

\acknowledgements
L.G.B.\ gladly acknowledges helpful discussions with
C Huang, M Soares-Furtado, ...
..., and is
grateful to the people who have turned TESS from an idea into reality.
%
J.N.W.\ thanks ...
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
This research has made use of the NASA Exoplanet Archive, which is
operated by the California Institute of Technology, under contract
with the National Aeronautics and Space Administration under the
Exoplanet Exploration Program.
%
This work made use of NASA's Astrophysics Data System Bibliographic
Services.
%
This research has made use of the VizieR catalogue access tool, CDS,
Strasbourg, France. The original description of the VizieR service was
published in A\&AS 143, 23.
%
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral
Agreement.
%
The Digitized Sky Surveys were produced at the Space Telescope Science Institute under U.S. Government grant NAG W-2166. The images of these surveys are based on photographic data obtained using the Oschin Schmidt Telescope on Palomar Mountain and the UK Schmidt Telescope. The plates were processed into the present compressed digital form with the permission of these institutions.
%
\newline
%
\facility{
	2MASS \citep{skrutskie_tmass_2006},
	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018},
	TESS \citep{ricker_transiting_2015},
	UCAC4 \citep{zacharias_fourth_2013}
    %DSS (CITE)    
}
%
\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  \texttt{astropy} \citep{the_astropy_collaboration_astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{astroquery.gaia} CITE,
  %\texttt{astroquery.simbad} CITE,
  %\texttt{astroquery.mast} CITE,
  %\texttt{astroquery.nasaexopanetarchive} CITE,
  \texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{corner} \citep{corner_2016},
  \texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{fitsh} \citep{Pal_2012},
  \texttt{IPython} \citep{perez_2007},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{serven_pygam_2018_1476122}
  \texttt{psycopg2} (\url{initd.org/psycopg})
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{scikit-learn} \citep{sklearn_2011},
  \texttt{TagSpaces} (\url{tagspaces.org}),
  \texttt{tesscut} \citep{brasseur_astrocut_2019},
  \texttt{VARTOOLS} \citep{Hartman_Bakos_2016}
  \texttt{wotan} \citep{hippke_wotan_2019},
}
